Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Reword description of Fischoff

\subsection{ROUGH: Methodology Motivation}

@@

\subsubsection{Technology Risk Perception} %LL: this text was previously inside related work
Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}. In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies. They were primed to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

>>>>

\subsection{Methodology Motivation}

@@

\subsubsection{Technology Risk Perception}
Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits of these technologies. They were told to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10).
We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.

%Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.
